%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ABSTRACT 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT} % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

\pagestyle{plain} % No headers, just page numbers
\pagenumbering{roman} % Roman numerals
\setcounter{page}{2}

\indent 
Virtualization is the technology powering today's cloud industry. With ubiquitous presence in the servers' and datacenters', it is now trying to penetrate the personal workstation market. Offering numerous benefits such as fault isolation, load balancing, faster server provisioning, etc virtualization occupies a dominant position in an IT infrastructure. 

Memory management suite is one of the core components of a hypervisor, and it has to adapt to the changing memory landscape. Current implementations assume the underlying memory technology to be homogenous and volatile. However, with the emergence of NVRAM in the form of Storage Class Memory, this assumption remains no longer valid. New motherboard architectures will support several different memory classes each with distinct properties and characteristics. The hypervisor has to recognize, manage, and expose them separately to the different virtual machines. This work mainly focusses on building a separate memory management pool for Non-Volatile RAM in Xen hypervisor. We further show that it can be efficiently implemented with minimal runtime performance overhead and code changes.
