%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.


\indent 

I would like to express my sincere gratitude to Prof. Reddy for his guidance and support during my graduate studies. 
This project was his brainchild, and he gave me this excellent opportunity to work on it and learn, despite my past inexperience in the subject area.
My time at Texas A\&M Univeristy has been very fruitful and enjoyable, largely due to his endless patience and compassion.
He stood as a shield protecting me from various adversities, arising more often than not, from my own immature decisions.
Prof. Reddy takes really good care of his students, protecting their academic as well as future professional interests, and I can never thank him enough. 
It is a matter of great pride and honour for me to complete my Master's thesis under his guidance.

This is also an excellent opportunity to thank our academic advisor, Ms. Tammy Carda, for her countless favors extended to every student.
She has extensive knowledge of the system rules and regulations, encompassing various departments such as ISS, OGS, etc. and makes seemingly impossible tasks look easy.
On several occasions, she went out of the way to help me and sort out my troubles, when the concerned department had given up.
Be it any problem or issue concerning the life of a graduate student, when presented to her, it disappears straigtaway.
The most surprising part is that, even after helping so many students, she is always available and only an email away.
It is my good fortune to have her as an academic advisor in our department.

I would also like to thank Gim Jongmin, Viacheslav Fedorov and Allen Webb for lending their technical expertise to this project. Jongmin, especially, gave many critical feedbacks and identified several potential problems early on, resulting in a better and mature design. 

Finally, I want to thank to my parents and my brother, who have constantly provided me with guidance, love and support, my entire life. I recognize the numerous sacrifices they make everyday for my sake, and hope that I can fill their life with joy and happiness as they have done so for me.

\pagebreak{}
